master thesis

### 2018-03-16 Paper - Latex/Paper - Skizze - v3.tex
Paper - rearrange subsections; add some new data for the simulation

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Multifurcation}
      We have a very high multifurcation rate (see results section \pageref{sec:ResultsMultifurcation}).
      Therefore, the impact of multifurcations on our research question has been investigated. \\
      Generalized Linear Models with poisson regression were compared according to their residuals and 
      BIC. \\
      \anmerkungstext{Nested models were compared using likelihood ratio tests, models using different 
        predictors were compared according to their deviance and AIC. (Emanuel)} \\
      \todo{Einfluss auf die Vorhersage des Castor und Fitch Algorithmus (Simulation)}

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{simulating loss of information of the tree topology}
      As previously explained, some divisions in the tree are not known, so the real tree is not binary.
        We simulate this multifurcation of the tree by \todo{...}.

      On the one hand, the strength of multifunctionation plays a role, as does the distribution. 
        Modeling was done as explained in \todo{sec x}.

      \todo{bisher ohne Begründung:!!!}
      we decided to use a $\frac{1}{x}$ distribution, where x is the depth of a node. This means, how 
      deaper we are, how less information we have. \\
      We traverse through the tree and pick a random number between 0 and 1. If random number is smaller 
        as our limit ($\frac{1}{x}$), than we forget the node and hang every child to the father node of 
        the current node. \\
      \anmerkung{poisson process $\rightarrow$ fit that distribution, include depth as a predictor, see if significant (Emanuel)}
      \begin{lstlisting}[gobble=6]
        def get_non_binary_tree(subtree, nodelist):
          i = 0
          while i != len(subtree.clades):
            if subtree.clades[i].is_terminal():             # is leaf node?
              i += 1
            else:
              element = Helpers.find_element_in_nodelist(subtree.clades[i].name, nodelist)
              limit = get_limit(element[1])
              new_random = random.uniform()                 # choose if we want to delete ourselve
              if new_random < limit:                        # or new_random < 0.9:
                subtree.clades += subtree.clades[i].clades  # add children
                del subtree.clades[i]                       # delete internal node
              else:                                         # if we don't deleted ourselve go on with children
                get_non_binary_tree(subtree.clades[i], nodelist)  # otherwise the children are in the current clade array
                i += 1
          return

          def get_limit(depth):
            limit = 1 - 1 / ((depth + 3) / 4)
            if limit < 0.1:
              limit = 0.1
            return limit
      \end{lstlisting}
      Wir lassen das Limit nicht beliebig klein werden, sondern beschränken es auf 0.1. \\

      With this loss of information the reconstruction can start.

@@

        At 90~\% unknown nodes, version 1 was 89.67~\%, version 2 was 89.67~\%, version 3 was 90.72~\%, 
          and version 4 was 90.74~\% correct. Therefore, only version 4 was used for all further 
          simulations.

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Results}
  A big point in this chapter is the result of examining the input data. How is the situation? What 
    influence does that have on our actual result? What can we do about it? Our simulation gave us 
    some results to this. \\
  Otherwise, this chapter is mainly about the actual reconstruction of the states. This means, on 
    one hand investigation of origins and losses of the inner nodes and on the other, the prediction 
    of unknown states of leaf nodes. \\
   
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Metadata analysis}

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Taxa}
      The investigation of the taxonomy revealed that our tree has three kingdoms: Chloroplastida, 
        Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
      Since the analysis of the tree is not part of this work, it should be mentioned here that, 
        according to recent findings, this is not complete and we lack some taxa in every rank. For 
        example, Hans says that one distinguishes between seven and nine kingdoms 
        \cite{CavalierSmith1981}. \\
      In section \pageref{subsec:listPhyla} of the appendix you can find a list of all phyla.

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \section{Multifurcation}\label{sec:ResultsMultifurcation}
      One property of the tree is its ridge of multifurcation. A complete phylogenetic tree would be 
        binary, which means the number of leaf nodes is closely to the number of internal nodes. But 
        since we only work with a synthesis tree, this tree is multifurcated: we have 241 974 internal 
        nodes and 2 293 463 leaf nodes. \\
      \begin{figure}[h]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
          \includegraphics[width=\textwidth]{Figures/multifurc.pdf}
          \caption{Histogram with automatic binwidth. \\ ~ \\ ~}
        \end{subfigure}
        ~~~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.42\textwidth}
          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=\textwidth]{Figures/multifurc_small.pdf}
          \caption{Histogram with $binwidth = 1$. \\ light blue: binary; dark blue: multifunction}
        \end{subfigure}
        \caption{Histograms about the multifurcation of the internal nodes of the synthesis tree.}
        \label{fig:childrenOfNodes}
      \end{figure}

      For a first overview we collected for every node its number of children (degree $-1$), and plotted
        this in two histograms, see figure \ref{fig:childrenOfNodes}. \\
      The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
        every node (a node with two children is binary). That means it discribes the number of nodes which we have lost from the real (binary) 
      phylogenetic tree. \\
      As you can see, we are very far from a binary tree.

@@

      %---------------------------------------------------------------------------------------------------
      %---------------------------------------------------------------------------------------------------
      \subsection{Poisson regression}
        glm (generalized linear model) analysis: \\

        The intercept is $2.821 > 0$ $\Rightarrow$ there is a multifunction.
        (Intercept: Stärke der Multifurcation) \\
        Comparing the different kingdoms, we find that multifunctionality is greater in Fungi than in 
        Chloroplastida than in Metazoa:
        $$4.0999 (Fungi Intercept) > -0.9132 (Chloroplastida Intercept) > -1.4320 (Metazoa Intercept)$$
        % Degrees of Freedom: 96010 Total (i.e. Null);  96010 Residual
        Wir haben außerdem drei komplexitätsstärken von Modellen verglichen bezüglich der höhe und tiefe 
          des Baums mit dem folgenden Deviance Table:

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Unknown leaf nodes}
    Next to the problem of the multifurcation of the tree is the less of data we have for the species.
      For the ancestral state reconstruction, we need information in the leaf nodes. \\
    The eukaryotic synthesis tree has 293 463 leaf nodes. The GloBI database has 5 346 414 interactions 
      (at this timepoint). Out of this data we got 51 337 distinct free-living species and 47 332 
      distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7~\%$). \\
    We found also $57,352$ (not distinct) source species and $809,993$ (not distinct) target
      species without OTT ids. Since we currently use only OTT ids, we could not use this information. \\
    \todo{With this only $\approx 4.3~\%$ information in our leaf nodes are ...} \\
    We also compared different models in terms of their BICs (Table: \ref{table:BIC unknown information}). 
      The Residuals are not very meaningful here, since all models have different dimensions.

@@

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            multifurc $\sim$ taxa & 545799 & \cellcolor{green!10}500004 & \cellcolor{green!50}485121 \\
            \hline
            multifurc $\sim$ taxa + depth & 544862 & \cellcolor{green!30}493808 & \cellcolor{green!50}481869 & 478851 \\
            \hline
            multifurc $\sim$ taxa * depth & 544179 & \cellcolor{green!50}489845 & \cellcolor{green!50}481494 \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{BICs of unknown information}
        \label{table:BIC unknown information} 
      \end{table}

@@

    \begin{figure}
      \centering
      \includegraphics[trim = 0mm 0mm 0mm 50mm, clip,width=0.9\textwidth]{Figures/simulation_evaluation_1.png}
      \caption{Influence of unknown data to prediction}
    \end{figure}

@@

      \todo{Castor replaces originaltags with finaltags. There are 82 originaltags != finaltag.} \\ \\

      We picked a few phyla to evaluate the results from the biological point of view. \\
      Table \ref{table:phylum leaf nodes states} shows some known phyla: Chordata, Nematoda, 
        Platyhelminthes and Apicomplexa. \\
      Since GloBI is not perfect, all examples contain a few bugs.
      As known the Chordata are full of free-living species and there are only a few parasites. Among 
        the birds are some breeding parasites (brood parasitism) like the cuckoo and clepto-parasites as 
        the skuas \cite{Rothschild1957}. The algorithm reflects this. We started with 99.83~\% 
        free-living species and predicted 99.94~\% species as parasites \todo{(inklusive all known nodes)}. 
        Only 0.06~\% were predicted as parasites. \\
      \todo{We found the cuckoo and some skuas...?} \\
      Same observation but with less free-livings is the Apicomplexa Phylum. Here we have only a few 
        free-livings \todo{ref einfügen}. And as we see, we had good start data and predicted 00.95~\% as 
        parasites. \\
      For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
        \todo{ref einfügen}. But at the end we predicted 4.18~\% as free-living. The class Seriata is the 
        reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
        the prediction looks right. \\
        \todotext{ Wiki: \\
        *The Seriata are an order of turbellarian flatworms.[1][2] \\
        They are found in both freshwater and marine environments, and also include a number of species 
        found in damp terrestrial conditions. Most are free-living, but the group includes the genus 
        Bdelloura, which lives comensally on the gills of horseshoe crabs. Seriatans are distinguished 
        from other related groups by the presence of a folded pharynx and of a number of diverticula 
        arising from the intestine. The intestine itself may be either simple or branched.[3]}

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Discussion}
  Wie gut ist der randomisiert erstellte Baum? \\
  Wie gut kommt unsere Simulation an die echte Datenlage heran. \\
  Fehlerqoute der Daten an sich? \\
  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit 
  Information. \\
  Simulation von subtrees \\
  Welche Teile des Baumes sind gut, an welchen muss noch viel geforscht werden. \\
  Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\

  Parameter der Simulation:
  \begin{itemize}
    \item Wie ist die Verteilung der vergessenen internen Knoten? Zum Wurzelknoten hin mehr vergessen?
    \item Wie sehen die übergangswahrscheinlichkeiten aus von P$\rightarrow$FL und andersherum?
    \item Verteilung Parasiten zu Freilebend zu keine Information
  \end{itemize}

  Selecting of the 'right'  / best Distribution

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Komplett aussortierte Tabellen etc}

  \begin{figure}
    \centering
    \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_Residuals.JPG}
    \caption{Crosstable of Residual values}
  \end{figure}

  \begin{figure}
    \centering
    \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.95\textwidth]{Figures/Kreuztabelle_BIC.JPG}
    \caption{Crosstable of BIC values}
  \end{figure}

  How to extend Fitch for multifunction?:
  \begin{figure}
    \centering
      \includegraphics[width=1\textwidth]{Figures/Fitch2.png}
  \end{figure}

>>>>

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Missing information}

      A binary tree with $n$ leaf nodes has $n-1$ internal nodes. The present Eukaryota tree of OTL has 
        2,293,463 leaf nodes and only 41,974 internal nodes, that is:
      $$100-\frac{100}{(2293463-1) \times 41974} \approx 98.16 \%$$
        missing internal nodes. \\

      % \anmerkungstext{Nested models were compared using likelihood ratio tests, models using different 
      %   predictors were compared according to their deviance and AIC. (Emanuel)} \\

      For the present Eukaryota tree with 2,293,463 leaf nodes, 34,869 free-livings and 25,962 parasites 
        are found, which are
        $$100-\frac{100}{2293463 \times (34860+25962)} \approx 97.34 \%$$
        unknown states of leaf nodes. \\

      In the simulation, the influence of the multifurcations and missing data in leaf nodes on the 
        predictive accuracy of the ancestral state reconstruction algorithms is tested. \\
      For the real data, generalized linear models are compared with poisson respectively binomial 
        regression according to their residuals and BICs.

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{simulating loss of information of the tree topology}
      As previously explained, some divisions in the tree are not known, so the real tree is not binary.
      This multifurcation was simulated by an equally distributed percentage of forgotten internal nodes.

@@

        At 90~\% unknown nodes and 90~\% of multifurcation of the internal nodes, version 1 was 89.26~\%, 
          version 2 was 89.26~\%, version 3 was 89.35~\%, and version 4 was 89.31~\% correct. Therefore, 
          only version 3 was used for all further simulations.

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Results}
  A big point in this chapter is the result of examining the input data. How is the situation? What 
    influence does that have on our actual result? What can we do about it? Our simulation gave us 
    some results to this. \\
  Otherwise, this chapter is mainly about the actual reconstruction of the states. This means, on 
    one hand investigation of origins and losses of the inner nodes and on the other, the prediction 
    of unknown states of leaf nodes. \\
   
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Metadata analysis}
    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Missing information}
      As previously presented, we have two types of missing information: unknown states of leaf nodes 
        and multifurcation. \\

      We examined the ridge of multifurcation of the tree. A complete phylogenetic tree would be 
        binary, which means the number of leaf nodes is closely to the number of internal nodes. But 
        since we only work with a synthesis tree, this tree is multifurcated: we have 241 974 internal 
        nodes and 2 293 463 leaf nodes. \\
      \begin{figure}[h]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
          \includegraphics[width=\textwidth]{Figures/multifurc.pdf}
          \caption{Histogram with automatic binwidth. \\ ~ \\ ~}
        \end{subfigure}
        ~~~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.42\textwidth}
          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=\textwidth]{Figures/multifurc_small.pdf}
          \caption{Histogram with $binwidth = 1$. \\ light blue: binary; dark blue: multifunction}
        \end{subfigure}
        \caption{Histograms about the multifurcation of the internal nodes of the synthesis tree.}
        \label{fig:childrenOfNodes}
      \end{figure}

      For a first overview we collected for every node its number of children (degree $-1$), and plotted
        this in two histograms, see figure \ref{fig:childrenOfNodes}. \\
      The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
        every node (a node with two children is binary). That means it discribes the number of nodes which we have lost from the real (binary) 
      phylogenetic tree. \\
      As you can see, we are very far from a binary tree. \\

      Some subtrees have been examined, these have the following percentages of missing information: See 
        table \ref{table:percentage loss information subtrees}.

      \begin{table} [h]
        \begin{center}
          \begin{tabular}{ |l|r|r||r|r|r| }
            \hline
            Domain  & \% unknown states & \% multifurcation \\ 
            / Kingdom  & (missing state information & (missing \\
            / Phylum / Class & of leaf nodes) & internal nodes) \\
            \hline \hline
            Eukaryota       & 97.34~\%  & 98.16~\% \\
            \hline \hline
            Metazoa         & 96.44~\%  & 87.93~\% \\ \hline
            Fungi           & 98.87~\%  & 96.97~\% \\ \hline
            Chloroplastida  & 99.14~\%  & 89.46~\% \\
            \hline \hline            
            Arthropoda      & 97.49~\%  & 89.95~\% \\ \hline
            Apicomplexa     & 86.26~\%  & 87.16~\% \\ \hline
            Nematoda        & 89.01~\%  & 88.59~\% \\ \hline
            Chordata        & 88.59~\%  & \cellcolor{green!50}66.49~\% \\ \hline
            Platyhelminthes & \cellcolor{green!50}68.73~\%  & 80.34~\% \\
            \hline \hline            
            Insecta         & 97.11~\%  & 90.78~\% \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{Examination of subtrees regarding missing information}
        \label{table:percentage loss information subtrees} 
      \end{table}

@@

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Taxa}
        The investigation of the taxonomy revealed that our tree has three kingdoms: Chloroplastida, 
          Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
        Since the analysis of the tree is not part of this work, it should be mentioned here that, 
          according to recent findings, this is not complete and we lack some taxa in every rank. For 
          example, Cavalier-Smith says that one distinguishes between seven and nine kingdoms 
          \cite{CavalierSmith1981}. \\
        In section \pageref{subsec:listPhyla} of the appendix you can find a list of all phyla.

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Poisson regression of the multifurcation}
        % glm (generalized linear model) analysis: \\
        The intercept is $2.821 > 0$ $\Rightarrow$ there is a multifunction.
        (Intercept: Stärke der Multifurcation) \\
        Comparing the different kingdoms, we find that multifunctionality is greater in Fungi than in 
        Chloroplastida than in Metazoa:
        $$4.0999 (Fungi Intercept) > -0.9132 (Chloroplastida Intercept) > -1.4320 (Metazoa Intercept)$$
        % Degrees of Freedom: 96010 Total (i.e. Null);  96010 Residual
        Wir haben außerdem drei komplexitätsstärken von Modellen verglichen bezüglich der höhe und tiefe 
          des Baums mit dem folgenden Deviance Table:

@@

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Binomial regression of the unknown state information}

        Next to the problem of the multifurcation of the tree is the less of data we have for the species.
          For the ancestral state reconstruction, we need information in the leaf nodes. \\
        The eukaryotic synthesis tree has 293 463 leaf nodes. The GloBI database has 5 346 414 interactions 
          (at this timepoint). Out of this data we got 51 337 distinct free-living species and 47 332 
          distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7~\%$). \\
        We found also $57,352$ (not distinct) source species and $809,993$ (not distinct) target
          species without OTT ids. Since we currently use only OTT ids, we could not use this information. \\
        \todo{With this only $\approx 4.3~\%$ information in our leaf nodes are ...} \\
        We also compared different models in terms of their BICs (Table: \ref{table:BIC unknown information}). 
          The Residuals are not very meaningful here, since all models have different dimensions.

@@

        \begin{table}[h!]
          \begin{center}
            \begin{tabular}{ |l|r|r|r|r| }
              \hline
              Model / Taxa & Kingdom & Phylum & Class & Order \\
              \hline \hline
              multifurc $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 & XXXXX \\
              \hline
              multifurc $\sim$ taxa + depth & \cellcolor{green!15}544862 & \cellcolor{green!40}493808 & \cellcolor{green!45}481869 & \cellcolor{green!50}478851 \\
              \hline
              multifurc $\sim$ taxa * depth & \cellcolor{green!15}544179 & \cellcolor{green!45}489845 & \cellcolor{green!45}481494 & \cellcolor{green!50}478188 \\
              \hline
            \end{tabular} 
          \end{center}
          \caption{BICs of unknown information}
          \label{table:BIC unknown information} 
        \end{table}

@@

    \begin{figure}[h!]
      \centering
      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.8\textwidth]{Figures/simulation_evaluation_1.png}
      \caption{Influence of unknown data to prediction}
    \end{figure}

@@

      \todo{Castor replaces originaltags with finaltags. There are 82 originaltags != finaltag.} \\

      We picked a few phyla to evaluate the results from the biological point of view. \\
      Table \ref{table:phylum leaf nodes states} shows some known phyla: Chordata, Nematoda, 
        Platyhelminthes and Apicomplexa. \\
      Since GloBI is not perfect, all examples contain a few bugs.

      \todo{\ref{table:table:percentage loss information subtrees}} \\

      As known the Chordata are full of free-living species and there are only a few parasites. Among 
        the birds are some breeding parasites (brood parasitism) like the cuckoo and clepto-parasites as 
        the skuas \cite{Rothschild1957}. The algorithm reflects this. We started with 99.83~\% 
        free-living species and predicted 99.94~\% species as parasites \todo{(inklusive all known nodes)}. 
        Only 0.06~\% were predicted as parasites. \\
      \todo{We found the cuckoo and some skuas...?} \\
      Same observation but with less free-livings is the Apicomplexa Phylum. Here we have only a few 
        free-livings \todo{ref einfügen}. And as we see, we had good start data and predicted 00.95~\% as 
        parasites. \\
      For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
        \todo{ref einfügen}. But at the end we predicted 4.18~\% as free-living. The class Seriata is the 
        reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
        the prediction looks right. \\
        \todotext{ Wiki: \\
        *The Seriata are an order of turbellarian flatworms.[1][2] \\
        They are found in both freshwater and marine environments, and also include a number of species 
        found in damp terrestrial conditions. Most are free-living, but the group includes the genus 
        Bdelloura, which lives comensally on the gills of horseshoe crabs. Seriatans are distinguished 
        from other related groups by the presence of a folded pharynx and of a number of diverticula 
        arising from the intestine. The intestine itself may be either simple or branched.[3]}

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Discussion}

  Fehlerqoute der Daten an sich? \\
  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit 
  Information. \\
  Welche Teile des Baumes sind gut, an welchen muss noch viel geforscht werden. \\
  Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\
  Es gibt noch ungenutze information in GloBI.

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Simulation}
    For fixed calculations we assume a distribution of 60\% free-living to 40\% parasites, 95\% 
      missing data and a multifuration rate of 95\%.
    How well does our simulation approach the real data situation? \\
    There are some points to discuss:
    \begin{itemize}
      \item How close is the randomized binary tree to a true phylogeny?
      \item The distribution of parasites to free-ranging species is a pure assumption. From different 
        sources about 40\% parasites are estimated, are these also beta-distributed?
      \item How well do the transition probabilities match parasitism? Depending on the type of 
        parasitism, this will certainly look different. In addition, it can be assumed that the 
        probability for losses is lower than for origins.
      \item The equal distribution of the multifurcation is a blank assumption. It is very likely to 
        be higher towards the root node because there is less information back in time. On the other 
        hand, there are many studies that have studied various species without considering phylogeny. 
        Which also creates a high number of children of a node directly at the leaf nodes.
    \end{itemize}
    In order to be able to observe these problems, we have programmed our simulation according to the 
      parameters. This allowed us to estimate the influence of some of these parameters.

@@
